---
title: "BrownProject_AH"
output: html_document
date: "2024-10-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download libraries

library(tidyverse)
library(data.table)
library(janitor)
library(readr)
library(ggplot2)
library(rstatix)
library(ggview)
library(readxl)
library(conflicted)
library(forcats) 
library(patchwork)

conflict_scout()
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::combine)
conflicts_prefer(dplyr::lag)
conflicts_prefer(data.table::transpose)

## Loading Data

setwd("/Users/ahuynh/downloads/BrownLab")
dat.tsv <- "/Users/ahuynh/downloads/BrownLab/EC_30K_GenomeMetadata.tsv"
dat <- fread(dat.tsv)
names(dat) <- make.names(names(dat), unique = T)

```{r Visualizing Quality Thresholds}

p.completeness <- ggplot(dat, aes(x=as.integer(CheckM.completeness))) + 
  xlim(90,100) + 
  geom_histogram(color="#2B2524", fill="#EE9E0A") + 
  theme_classic() +
  geom_vline(xintercept = 98, linetype="solid", color = "#FD0207", size=1) +
  annotate(geom="label", x=96.75, y=2000, label="Cut off at 98%", color="white", fill = "#FD0207") +
  xlab("% Completeness") +
  ylab("Number of Genomes") +
  theme_classic()

p.Contamination <- ggplot(dat, aes(x=as.integer(CheckM.contamination))) + 
  xlim(-1,10) + 
  geom_histogram(color="#2B2524", fill="#EE9E0A") + 
  theme_classic() +
  geom_vline(xintercept = 2, linetype="solid", color = "#FD0207", size=1) +
  annotate(geom="label", x=3.2, y=2000, label="Cut off at 2%", color="white", fill = "#FD0207") +
  xlab("% Contamination") +
  ylab("Number of Genomes")

p.Genome.size <- ggplot(dat, aes(x=as.integer(Assembly.Stats.Total.Ungapped.Length)/1000)) + 
  geom_histogram(color="#2B2524", fill="#EE9E0A") + 
  theme_classic() +
  xlab("Genome Size (Kb)") +
  ylab("Number of Genomes")

p.contigs <- ggplot(dat, aes(x=as.integer(Assembly.Stats.Number.of.Contigs))) + 
  geom_histogram(color="#2B2524", fill="#EE9E0A") + 
  theme_classic() +
  geom_vline(xintercept = 300, linetype="solid", color = "#FD0207", size=1) +
  annotate(geom="label", x=625, y=2000, label="Cut off at 300 contigs", color="white", fill = "#FD0207") +
  xlab("Number of Contigs") +
  ylab("Number of Genomes")

p.N50 <- ggplot(dat, aes(x=as.integer(Assembly.Stats.Contig.N50))) + 
  geom_histogram(color="#2B2524", fill="#EE9E0A") + 
  theme_classic() +
  geom_vline(xintercept = 100000, linetype="solid", color = "#FD0207", size=1) +
  annotate(geom="label", x=1000000, y=2000, label="Cut off at 100kb", color="white", fill = "#FD0207") +
  xlab("N50") +
  ylab("Number of Genomes")


p.completeness
p.Contamination
p.Genome.size
p.contigs
p.N50

```

dat %>% select(Assembly.BioSample.Isolation.source) %>% unique() # look at all the unique entries in Isolation.source column

# Making preliminary plot based on disease counts
dat %>% na.omit() %>% 
  filter(!Assembly.BioSample.Host.disease %in% c("", "not collected", "Not collected", "not applicable", "missing", "Unknown", "Missing")) %>% 
  count(Assembly.BioSample.Host.disease) %>% # count for each unique entry of host disease
  arrange(-n) %>% # arrange in desc order by count
  filter(n > 10) %>% # filter where count > 10
  ggplot(aes(x = reorder(Assembly.BioSample.Host.disease, desc(n)), y = n)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
  

completness <- 98 # Not all genomes have this
contamination <- 2 # Not all genomes have this
contigs <- 300
n.50 <- 100000
  
# Make a base dataset filtering by contig and n.50 thresholds
dat_all <- dat %>%
  filter(Assembly.Stats.Number.of.Contigs <= contigs & Assembly.Stats.Contig.N50 >= n.50)
  
# Make from base dataset another dataset of those that passed the CheckM completeness and contamination thresholds
dat.passed <- dat_all %>%
  filter(CheckM.completeness >= completness & CheckM.contamination <= contamination)

# Niche Categorization


niche_categorize <- function(data) {
    data %>%
    
    mutate(Niche = case_when(
    grepl("urine|urinary tract infection|Clean-catch urine sample|clinical urine culture|urine cath|UTI|urine culture|urine       cathether|urine from Syrian refugee|Urine sample", Assembly.BioSample.Isolation.source, ignore.case = TRUE) | 
    grepl("UTI|Kidney failure|Urinary Tract Infection|Urinary tract infection|Urinary Tracts Infection",                 Assembly.BioSample.Host.disease, ignore.case = TRUE) ~ "Urinary",
    grepl("child cystic", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "early.CF",
    grepl("cf|cystic|fibrosis", Assembly.BioSample.Isolation.source, ignore.case = TRUE) | 
    grepl("cf|cystic|fibrosis", Assembly.BioSample.Host.disease, ignore.case = TRUE) ~ "CF",
    grepl("bile|Bile fluid", Assembly.BioSample.Isolation.source, ignore.case = TRUE) | 
    grepl("end-stage liver disease", Assembly.BioSample.Host.disease, ignore.case = TRUE) ~ "Bile",
    grepl("bacteremia|sepsis|blood stream infection|Blood|blood from patient with pneumonia|blood fluid|bloodstream", Assembly.BioSample.Isolation.source, ignore.case = TRUE) | 
    grepl("blood|sepsis|bloodstream infection|Blood stream infection", Assembly.BioSample.Host.disease, ignore.case = TRUE) ~ "Blood",
    grepl("wound sectretion|sore|abscess|tissue|ulcer|lesion|sternal wound|wound|soldier combat wound|Wound secretion|wound abscess|surgical wound", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Wound",
    grepl("skin swab|cutaneus swab|skin and soft tissue|Damaged skin", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Skin",
    grepl("respiratory secretions|Pneumonia|pneumonia|respiratory secretion", Assembly.BioSample.Isolation.source, ignore.case = TRUE) | 
    grepl("Pneumonia|pneumonia|Bacterial Pneumonia", Assembly.BioSample.Host.disease, ignore.case = TRUE) ~ "Pneumonia",
    grepl("Sputamentum|sputum|sputum from patient with respiratory tract infection", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Sputum",
    grepl("perianal swab|perianal|anal|perianal isolate|anal swab|rectal|Rectal swab|Perirectal|Rectum|rectum|perirectal|rectal swab", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Rectal/Anal",
    grepl("vitreous fluid from young man|patient fluids|purulent material|excreted bodily substance|bodily fluid|pus|Secreta|abscess|abdominal drainage fluid|Drainage samples from liver abscess|cerebrospinal fluid|penile discharge|cerebrospinal fluid|miscellaneous body fluid", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Bodily fluid/pus",
    grepl("human", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Human",
    grepl("bronchial|lower respiratory|bronch|trach|airway|alveolar|copd|lung|Bronchoscopy|Tracheal aspiration|pleural fluid|Bronchail secretion|bronchoalveolar lavage|Endobronchail swabBroncho-Alveolar Lavage|respiratory|Airway specimen|Tracheal secretion|endotracheal aspirate", Assembly.BioSample.Isolation.source, ignore.case = TRUE) | 
    grepl("pleumonia", Assembly.BioSample.Host.disease, ignore.case = TRUE) ~ "Respiratory/Lungs",
    grepl("throat|Expectorate|throat swab|pharynx", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Throat",
    grepl("Perineum", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Perineum",
    grepl("ventilator|bed sheets|telephone of Nurse station|hospital|OP|clinical sample|patient room|hospital room swab|patient|bedside|rail|vent|nebuliser|treatment|nursing|button|ecg|syringe|icu|Abdominal drain tube|Central venous line|abdominal drainage|catheter tip|central venous catheter|Abdominal Abscess|lumbar drain tip", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Hospital",
    grepl("Ear secretion", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Ear",
    grepl("Thigh tissue", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Thighs",
    grepl("soil|sand|dirt|agricultural field soil|soil|environment contaminated by Homo sapiens patients", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Terrestrial",
    grepl("Environemnt", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Environment",
    grepl("water|pipe|spring|lilypad|puddle|saltern|pool|pond|stream|surface water|urban river waters|river water|water sample from urban lake", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Aquatic",
    grepl("jejunal aspirate|gut", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Intestine",
    grepl("Vagina|endocervical swab", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Vagina/Cervix",
    grepl("nose|nasal swab|sinus|nasal|nasopharynx", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Upper Respiratory",
    grepl("Korean infant feces|fecal sample|stool|fecal swab|feces|fecal", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Feces",
    grepl("garam masala hot spice mixture|retail chicken|Carrots|vegetable|milk|Parsley|Celery|Mint|tomato|carrot|Lettuce|Beet", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Food/Drinks",
    grepl("Industrial effluent", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Industry",
    grepl("Femoral bone", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Bone",
    grepl("laboratory strain", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Lab strain",
    grepl("runoff|pharma|waste|sewage|sludge|Wastewater Influent|Wastewater Effluent|Domestic sewage|drainage|wastewater|hospital sewage|the activated sludge of Harbin Taiping wastewater treatment plant|chromate-containing wastewater", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Sewage/Wastewater",
    grepl("neck", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Neck",
    grepl("urethral swab", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Urethra",
    grepl("gall|Gall bladder|gallbladder isolate|Gall Bladder|Fluid gall bladder|Gallbladder Abscess", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Gall",
    grepl("Liver cyst|\\bcyst\\b", Assembly.BioSample.Isolation.source, ignore.case = TRUE) | 
    grepl("Cystitis|acute cystitis", Assembly.BioSample.Host.disease, ignore.case = TRUE) ~ "Cyst",
    grepl("Diaphragm tissue|skin and soft tissue", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Tissue",
    grepl("shower|kitchen|drain|toilet|drinking|fountain|humidifier|metal|wood|plastic|truck swab|Sink", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Built Environment",
    grepl("brain|brain bleed|brain Hemorrhage|Brain infraction|brain abscess|Brain congestion", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Brain",
    grepl("cloacal swab|dog with urinary tract infection|wild-caught Atlantic blue crabs|animal|dog|cat|fish|dolphin|chicken|poultry|canine|pork|pig|veterinary|Turkey cecum|rugao ham", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Animal",
    grepl("Burn Patient", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Burn",
    grepl("eye|cornea|conjunctiva", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Eye",
    grepl("ocean|sea|submarine", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Ocean",
    grepl("plant|root|rhizo|tree|pepper|tomato|potato|onion|leaf|fruit|lettuce", Assembly.BioSample.Isolation.source, ignore.case = TRUE) ~ "Plant",
    TRUE ~ NA_character_
  ))

}

# Note: NA comprises of both those explicitly denoted as missing and those that do not fall under our current niche classifications


dat.niches <- niche_categorize(dat_all) # Niche df of all
dat.niches.passed <- niche_categorize(dat.passed) # Niche df only CheckM passed

```{r}
dat.niches.passed %>% filter(!is.na(Niche)) %>%
  count(Niche) %>%
  ggplot(aes(x = reorder(Niche, desc(n)), y = n)) +
  geom_bar(stat = "identity") +
  labs(title = "Niche Plot of E.Coli that Passed CheckM Thresholds", x = "Niche", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

```

# Writing genomes that passed CheckM and has a niche into csv file
# dat.final is a df of genomes that passed CheckM and have a Niche assigned
dat.final <- dat.niches.passed %>% filter(!is.na(Niche))

# Writing genomes to download into a csv file
dat.final %>% write_csv("/Users/ahuynh/downloads/BrownLab/01_Filter_New_Genomes_EC_30K_niche_metadata_UnFiltNiches.csv")


# ____ Plot: Proportion of each niche value over total genomes (for each pathogen in one plot)
# Make a plot for each of the ESKAPE where its the proportion of the top 5 main niches and the 6th being all other

# ____ Terminal code: Write script to download genomes (genomes remove the missing samples)


# ____ Plot: Stacked bar plot of passed vs non-passed CheckM among thos that passed CheckM Thresholds

checkm_df <- dat.niches %>%
  group_by(Niche) %>%
  filter(
  !is.na(CheckM.completeness) &
  !is.na(CheckM.contamination)
  )

# Among those with checkm, look at if they meet the CheckM completeness and contamination
# added another column where 1 = passed checkm and 0 = did not pass checkm
checkm_passed_df <- checkm_df %>% filter(!is.na(Niche)) %>%
  mutate(checkm_status_passed = as.integer(CheckM.completeness >= completness & CheckM.contamination <= contamination))
   
checkm_passed_summary <- checkm_passed_df %>%
    count(Niche, checkm_status_passed)
    
palette.colors(palette = "R4") # getting good colorblind friendly palettes

```{r} 
# info about CheckM

# Contamination = 0 indicates that the genome assembly is considered "clean" with no detected contamination. This suggests that the genome consists entirely of sequences attributed to a single species without any extraneous sequences from other organisms.

# Contamination = NA indicates that CheckM has not been able to compute or assign a contamination value. It's not possible to determine whether the genome is clean or contaminated based on this.

# Completeness ~ completeness refers to how much of a genome is present in a given sample or assembly.

# >= 98% completeness + <=2% contamination

```

```{r}
ggplot(checkm_passed_summary, aes(x = fct_reorder(Niche, n, .desc = TRUE), fill = as.factor(checkm_status_passed))) +
    geom_bar(aes(y = n), position = "stack", stat = "identity") +
    ylab("Count") +
    xlab("Niche") +
    theme_minimal() +
    labs(fill = "CheckM Status", title = "Count of E. coli Genomes Based on CheckM Threshold") +
    scale_fill_manual(values = c("0" = "#DF536B", "1" = "#61D04F"),  # Customize colors
                      labels = c("0" = "Not Passed", "1" = "Passed")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# getting only the top 5 niches and everything else is turned to other

total_niche_count <-checkm_passed_summary %>%
    group_by(Niche) %>%
    summarise(total_count = sum(n)) %>%
    arrange(desc(total_count)) 


# create vector with the top 5 niches
replace_list <- total_niche_count$Niche[1:5] # can't do total_niche_count[1:5,] bc that gives df not vector which comparison of values works better for

overall_total_count <- sum(total_niche_count$total_count)


mod5_checkm_passed_summary <- total_niche_count %>%
  mutate(Niche = ifelse(Niche %in% replace_list, Niche, "Other")) %>%
  group_by(Niche) %>%
  summarise(total_count = sum(total_count)) %>%
   mutate(total_count = total_count / overall_total_count) %>%
  arrange(desc(total_count))


# Load the necessary library
library(RColorBrewer)

# Ensure you have enough unique colors for each category
n_colors <- length(unique(mod5_checkm_passed_summary$Niche))
unique_colors <- brewer.pal(n = min(n_colors, 12), name = "Set3")


# Plot with unique colors

library(ggplot2)
library(forcats)  # Ensure you have the forcats package for fct_reorder


ggplot(mod5_checkm_passed_summary, aes(x = "", fill = fct_reorder(Niche, -total_count))) + 
  geom_bar(aes(y = total_count), position = "stack", stat = "identity") + 
  ylab("Proportion") + 
  xlab("E. Coli") +  # Set x-axis label to empty 
  theme_minimal() + 
  labs(fill = "Niche") + 
  theme(legend.position = "none") +  # Remove the legend
  scale_fill_manual(values = unique_colors) + 
  geom_text(aes(y = total_count, label = Niche), size = 3, 
            position = position_stack(vjust = 0.5), 
            color = "black") 
            
# below version removes y axis and y title
ggplot(mod5_checkm_passed_summary, aes(x = "", fill = fct_reorder(Niche, -total_count))) + 
  geom_bar(aes(y = total_count), position = "stack", stat = "identity") + 
  ylab("Proportion") + 
  xlab("E. Coli") +  # Set x-axis label to empty 
  theme_minimal() + 
  labs(fill = "Niche") + 
  theme(legend.position = "none", axis.text.y=element_blank(), axis.title.y=element_blank()) +  # Remove the legend
  scale_fill_manual(values = unique_colors) + 
  geom_text(aes(y = total_count, label = Niche), size = 3, 
            position = position_stack(vjust = 0.5), 
            color = "black") 
            

# Manually making color palettes so common niches are the same color

# Blood, Other, Feces, Urinary, Rectal, Aquatic (E faecium)
color_5 <- c("#80B1D3","#FFFFB3","#8DD3C7","#BEBADA","#FB8072","#FC8D62")

# Blood, Other, Upper respiratory, Wound, SPutum, Food/drinks (S aureus)
color_6 <- c("#80B1D3","#FFFFB3","#984EA3","#BC80BD","#B3DE69", "#A6D854")

# Other, blood, urinary, sputum, respiratory/lungs, feces
color_7 <- c("#FFFFB3","#80B1D3","#FFED6F","#B3DE69","#FCCDE5","#8DD3C7")


# Feces, Other, Urinary, Rectal, Blood, Animal (E Coli)
color_1 <- c("#8DD3C7", "#FFFFB3", "#BEBADA", "#FB8072", "#80B1D3", "#FDB462")
# Sputum, Other, Blood, Respiratory/Lungs, Pneumonia, Wound (A Baunmii)
color_2 <- c("#B3DE69","#FFFFB3", "#80B1D3", "#FCCDE5", "#D9D9D9", "#BC80BD")
# Other, CF, Sputum, Blood, Urinary, Respiratory/Lungs (P aeru)
color_3 <- c("#FFFFB3", "#CCEBC5", "#B3DE69", "#80B1D3", "#FFED6F", "#FCCDE5")
# Feces, Terrestrial, Aquatic, Sewage/Wastewater (Enterbacter Sp)
color_4 <- c("#8DD3C7", "#FFFF33", "#FC8D62", "#8DA0CB")



# Set3: "#8DD3C7" "#FFFFB3" "#BEBADA" "#FB8072" "#80B1D3" "#FDB462" "#B3DE69" "#FCCDE5" "#D9D9D9" "#BC80BD" "#CCEBC5" "#FFED6F"

# Set2: "#66C2A5" "#FC8D62" "#8DA0CB" "#E78AC3" "#A6D854" "#FFD92F" "#E5C494" "#B3B3B3"

# Set1: "#E41A1C" "#377EB8" "#4DAF4A" "#984EA3" "#FF7F00" "#FFFF33" "#A65628" "#F781BF" "#999999"

# Get all colors from the Set3 palette
# set3_colors <- brewer.pal(n = 12, name = "Set1")

# Print the colors
# print(set3_colors)


#______________ Creating a function that will extract necessary values to create proportion plot______________

agg_1 <- function(file_path, name, plot_condition, color_palette) {

    dat.tsv <- file_path
    dat <- fread(dat.tsv)
    names(dat) <- make.names(names(dat), unique = T)
    
    completness <- 98 # Not all genomes have this
    contamination <- 2 # Not all genomes have this
    contigs <- 300
    n.50 <- 100000
    
    dat_all <- dat %>%
    filter(Assembly.Stats.Number.of.Contigs <= contigs & Assembly.Stats.Contig.N50 >= n.50)
    dat.niches <- niche_categorize(dat_all) # Niche df of all
    
    checkm_df <- dat.niches %>%
    group_by(Niche) %>%
    filter(
    !is.na(CheckM.completeness) &
    !is.na(CheckM.contamination))
    
    
    checkm_passed_df <- checkm_df %>% filter(!is.na(Niche)) %>%
    mutate(checkm_status_passed = as.integer(CheckM.completeness >= completness & CheckM.contamination <= contamination))
   
    checkm_passed_summary <- checkm_passed_df %>%
    count(Niche, checkm_status_passed)
    
    
    # getting only the top 5 niches and everything else is turned to other

    total_niche_count <-checkm_passed_summary %>%
    group_by(Niche) %>%
    summarise(total_count = sum(n)) %>%
    arrange(desc(total_count)) 


    # create vector with the top 5 niches
    replace_list <- total_niche_count$Niche[1:5] # can't do total_niche_count[1:5,] bc that gives df not vector        which comparison of values works better for

    overall_total_count <- sum(total_niche_count$total_count)


    mod5_checkm_passed_summary <- total_niche_count %>%
    mutate(Niche = ifelse(Niche %in% replace_list, Niche, "Other")) %>%
    group_by(Niche) %>%
    summarise(total_count = sum(total_count)) %>%
    mutate(total_count = total_count / overall_total_count) %>%
    arrange(desc(total_count))
    
    
    
    # Ensure you have enough unique colors for each category
    #n_colors <- length(unique(mod5_checkm_passed_summary$Niche))
    #unique_colors <- brewer.pal(n = min(n_colors, 12), name = "Set3")

    if (plot_condition) {
    # Plot with unique colors
    res_plot <- ggplot(mod5_checkm_passed_summary, aes(x = "", fill = fct_reorder(Niche, -total_count))) + 
    geom_bar(aes(y = total_count), position = "stack", stat = "identity") + 
    ylab("Proportion") + 
    xlab(name) +  # Set x-axis label to empty 
    theme_minimal() + 
    labs(fill = "Niche") + 
    theme(legend.position = "none") +  # Remove the legend
    scale_fill_manual(values = color_palette) + 
    geom_text(aes(y = total_count, label = Niche), size = 3, 
            position = position_stack(vjust = 0.5), 
            color = "black") 
    } else {
    
    
    res_plot <- ggplot(mod5_checkm_passed_summary, aes(x = "", fill = fct_reorder(Niche, -total_count))) + 
    geom_bar(aes(y = total_count), position = "stack", stat = "identity") + 
    ylab("Proportion") + 
    xlab(name) +  # Set x-axis label to empty 
    theme_minimal() + 
    labs(fill = "Niche") + 
    theme(legend.position = "none", axis.text.y=element_blank(), axis.title.y=element_blank()) +  # Remove the        legend
    scale_fill_manual(values = color_palette) + 
    geom_text(aes(y = total_count, label = Niche), size = 3, 
            position = position_stack(vjust = 0.5), 
            color = "black") 
    


  }
            
    return(res_plot)
    
}

``` {r Running aggregate plot functions}

EF_plot <- agg_1("/Users/ahuynh/downloads/BrownLab/EF_30K_GenomeMetadata.tsv", "E. faecium", TRUE, color_5)
SA_plot <- agg_1("/Users/ahuynh/downloads/BrownLab/SA_30K_GenomeMetadata.tsv", "S. aureus", FALSE, color_6)
KP_plot <- agg_1("/Users/ahuynh/downloads/BrownLab/KP_30K_GenomeMetadata.tsv", "K. pneumoniae", FALSE, color_7)
AB_plot <- agg_1("/Users/ahuynh/downloads/BrownLab/AB_30K_GenomeMetadata.tsv", "A. baumannii", FALSE, color_2)

PA_plot <- agg_1("/Users/ahuynh/downloads/BrownLab/PA_30K_GenomeMetadata.tsv", "P. aeruginosa", TRUE, color_3)
ESP_plot <- agg_1("/Users/ahuynh/downloads/BrownLab/ESP_30K_GenomeMetadata.tsv", "Enterobacter Sp.", FALSE, color_4)
EC_plot <- agg_1("/Users/ahuynh/downloads/BrownLab/EC_30K_GenomeMetadata.tsv", "E. coli", FALSE, color_1)


# Combining the plot (via pathwork library)
ESKAPEE_combined_plot <- EF_plot + SA_plot +KP_plot + AB_plot + PA_plot + ESP_plot + EC_plot +
plot_layout(ncol = 4) + 
    plot_annotation(title = "Proportion of ESKAPEE by Dominating Niches", 
                    theme = theme(plot.title = element_text(hjust = 0.5)))

```

``` {r}

EF_plot
SA_plot
KP_plot
AB_plot
PA_plot
ESP_plot
EC_plot
ESKAPEE_combined_plot

```

#___ getting the proportion bar plot but split by isolation source

